Figures

### 2018-09-26 figures/02_conny_metric_key.tex
emphasize connectivity differences

    \begin{column}{0.25\textwidth}
      \vspace{1em}
      \begin{tikzpicture}[scale = 2]
        %\draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
        \draw [-,ultra thick, cyan] (1.8,2.6) to [out=180,in=0] (1.1,1.9) to [out=270,in=90] (0,0);        
        \draw [-,ultra thick, cyan] (0.5,2.9) to [out=0,in=90] (1.1,1.9) to [out=270,in=90] (0,0);

        \draw [-,ultra thick, cyan] (-1.2,3.4) to [out=200,in=0] (-1.8,2.4) to [out=290,in=110] (-1.1,1.9) to [out=270,in=90] (0,0);        
        \draw [-,ultra thick, cyan] (-0.5,2.9) to [out=250,in=70] (-1.1,1.9) to [out=270,in=90] (0,0);

@@

    \begin{column}{0.25\textwidth}
      \begin{tikzpicture}[scale = 2]
          % \draw[step=1cm,gray,very thin] (-4,-4) grid (4,4);
          \draw [-,ultra thick, cyan] (2.2,4.8) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
          \draw [-,ultra thick, cyan] (0.9,4) to [out=290,in=0] (1.1,1.9) to [out=270,in=90] (0,0);

          \draw [-,ultra thick, cyan] (2.4,3.4) to [out=290,in=40] (1.95,3);
          \draw [-,ultra thick, cyan] (0.5,4.1) to [out=310,in=190] (1,3.8);
          \draw [-,ultra thick, cyan] (1.8,4.4) to [out=290,in=70] (2.12,4);

@@

    \begin{column}{0.25\textwidth}
    \vspace{1em}
      \begin{tikzpicture}[scale = 2]
        % \draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
        \draw [-,ultra thick, cyan] (2,3) to [out=180,in=0] (1.1,1.9) to [out=270,in=90] (0,0);        
        \draw [-,ultra thick, cyan] (0.5,2.9) to [out=0,in=90] (1.1,1.9);
        \draw [-, line width = 7pt, cyan] (1.1,1.9) to [out=270,in=90] (0,0);
        \draw [-,ultra thick, cyan] (1.8, 2.1) to [out=290,in=0] (1,1.5);

>>>>

    \begin{column}{0.25\textwidth}
      \vspace{3em}
      \begin{tikzpicture}[scale = 2]
        %\draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
        \draw [-,ultra thick, cyan] (1.6,2.4) to [out=180,in=0] (1.1,1.9) to [out=270,in=90] (0,0);        
        \draw [-,ultra thick, cyan] (0.58,2.3) to [out=0,in=90] (1.1,1.9) to [out=270,in=90] (0,0);

        \draw [-,ultra thick, cyan] (-1.2,2.75) to [out=200,in=0] (-1.6,2.4) to [out=290,in=110] (-1.1,1.9) to [out=270,in=90] (0,0);        
        \draw [-,ultra thick, cyan] (-0.58,2.3) to [out=250,in=70] (-1.1,1.9) to [out=270,in=90] (0,0);

@@

    \begin{column}{0.25\textwidth}
      \begin{tikzpicture}[scale = 2]
          %\draw[step=1cm,gray,very thin] (-4,-4) grid (4,4);
          \draw [-,ultra thick, cyan] (2.2,4.8) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
          \draw [-,ultra thick, cyan] (0.9,4) to [out=290,in=0] (1.1,1.9) to [out=270,in=90] (0,0);

          \draw [-,ultra thick, cyan] (2.9,3.4) to [out=290,in=40] (1.95,3);
          \draw [-,ultra thick, cyan] (0.2,3.9) to [out=310,in=190] (1.25,3.2);
          \draw [-,ultra thick, cyan] (1.6,4.8) to [out=290,in=85] (2.07,3.6);

@@

    \begin{column}{0.25\textwidth}
    \vspace{2em}
      \begin{tikzpicture}[scale = 2]
        % \draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
        \draw [-,ultra thick, cyan] (2,3) to [out=180,in=0] (1.1,1.9) to [out=270,in=90] (0,0);        
        \draw [-,ultra thick, cyan] (0.5,2.9) to [out=0,in=90] (1.1,1.9);
        \draw [-, line width = 7pt, cyan] (1.1,1.9) to [out=270,in=90] (0,0);
        \draw [-,ultra thick, cyan] (1.8, 2.1) to [out=290,in=0] (1,1.5);
